Estimating individual subjective values of emotion regulation strategies

### 2023-04-21 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex

To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) was specified using the \(lmerTest\) package\textsuperscript{67}.
First, ER strategies were recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
Restricted maximum likelihood (REML) was applied to fit the model.
A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), utility (utility ratings), and physiological responses (\emph{corrugator} and \emph{levator} activity) as level-1-predictors was specified.
\[
\begin{split}
SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (strategy|subject)
\end{split}
\]
Level-1-predictors were centered within cluster\textsuperscript{68}.
Residuals of the final model were inspected visually.
Intraclass correlation coefficient (ICC), \(\rho\), was reported for each model (null model, as well as full model).
The presented MLM followed the conceptualization of Zerna, Scheffel, et al.\textsuperscript{34}

>>>>

To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) was specified using the \(lmerTest\) package\textsuperscript{67}.
First, ER strategies were recoded and centered for each subject according to their individual SVs: The strategy with the highest SV was coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV was coded as 1.
Restricted maximum likelihood (REML) was applied to fit the model.
A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), utility (utility ratings), and physiological responses (\emph{corrugator} and \emph{levator} activity) as level-1-predictors was specified.
\[
\begin{split}
SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (strategy|subject)
\end{split}
\]
Level-1-predictors were centered within cluster\textsuperscript{68}.
Residuals of the final model were inspected visually.
Intraclass correlation coefficient (ICC), \(\rho\), was reported for each model (null model, as well as full model).
The presented MLM followed the conceptualization of Zerna, Scheffel, et al.\textsuperscript{34}

### 2023-04-21 06_Paper/ER-ED/ERED_Stage2/method.Rmd

To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) was specified using the $lmerTest$ package[@Kuznetsova2017].
First, ER strategies were recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
Restricted maximum likelihood (REML) was applied to fit the model.
A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), utility (utility ratings), and physiological responses (*corrugator* and *levator* activity) as level-1-predictors was specified.
$$
\begin{split}
SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (strategy|subject)
\end{split}
$$ 
Level-1-predictors were centered within cluster[@Enders2007].
Residuals of the final model were inspected visually.
Intraclass correlation coefficient (ICC), $\rho$, was reported for each model (null model, as well as full model).
The presented MLM followed the conceptualization of Zerna, Scheffel, et al.[@ZernaScheffel2022]

>>>>

To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) was specified using the $lmerTest$ package[@Kuznetsova2017].
First, ER strategies were recoded and centered for each subject according to their individual SVs: The strategy with the highest SV was coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV was coded as 1.
Restricted maximum likelihood (REML) was applied to fit the model.
A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), utility (utility ratings), and physiological responses (*corrugator* and *levator* activity) as level-1-predictors was specified.
$$
\begin{split}
SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (strategy|subject)
\end{split}
$$ 
Level-1-predictors were centered within cluster[@Enders2007].
Residuals of the final model were inspected visually.
Intraclass correlation coefficient (ICC), $\rho$, was reported for each model (null model, as well as full model).
The presented MLM followed the conceptualization of Zerna, Scheffel, et al.[@ZernaScheffel2022]
